Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex
Fix it
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

In this section we consider several extensions to our IFC system.
%
Specifically, we discuss how the specification language can be
extended to consider other IFC-aware features (e.g., fine-grained
labeled values), a static type system, or more complex scheduling
policies.
%
When considering these extensions we also highlight some limitations
of our approach.

@@

Different concrete IFC implementations may wish to extend our minimal
system with labeled constructs appropriate for their envisioned
applications.
%
For example, SWAPI provides a labeled version of the XHR object, while
LIO implements a labeled file system, use in severer-side web
applications~\cite{hails}.
%
However, since proving non-interference for a concrete implementation
follows by isomorphism to the specification language, below we
consider the addition of several labeled constructs to the latter.
%
We remark that that the non-interference proofs must account for the
new constructs, since they amend the IFC calculus semantics (usually
by addition).

>>>>

In this section we consider several extensions to our IFC system.
%
Specifically, we discuss how the specification language can be
extended to consider other IFC-aware features (e.g., fine-grained
labeled values), a static type system, or more complex scheduling
policies.
%
When considering these extensions we also discuss some limitations
of our approach.

@@

Different concrete IFC implementations may wish to extend our minimal
system with labeled constructs appropriate for their envisioned
applications.
%
For example, SWAPI provides a labeled version of the XHR object, while
LIO implements a labeled file system, use in server-side web
applications~\cite{hails}.
%
Below we
consider the addition of several labeled constructs to the abstract specification.
%
We remark that that the non-interference proofs must account for the
new constructs, since they amend the IFC calculus semantics (usually
by addition).
